An open-source integrated framework for the automation of citation collection and screening in systematic reviews.

### 2022-01-24 Manuscript/Manuscript.tex
small corrections

\author{
    Angelo D'Ambrosio
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:angelo.d.ambrosio@uniklinik-freiburg.de}{\nolinkurl{angelo.d.ambrosio@uniklinik-freiburg.de}};
\href{mailto:a.dambrosioMD@gmail.com}{\nolinkurl{a.dambrosioMD@gmail.com}}} \\
   \And
    Tjibbe Donker
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:tjibbe.donker@uniklinik-freiburg.de}{\nolinkurl{tjibbe.donker@uniklinik-freiburg.de}}} \\
   \And
    Hajo Grundmann
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
  }

@@

\begin{abstract}
The exponential growth in scientific production makes its summarisation
through secondary literature exceedingly demanding in terms of time and
human resources. We introduce a new open-source framework that
significantly increases efficiency during the citation collection and
screening phases of systematic reviews.\\
The framework introduces three main tools: 1) an automatic citation
search engine and manager that allows collecting records from multiple
citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified
query syntax; 2) a citation screening tool based on Bayesian active
machine learning and natural language processing, which requires users
feedback only on uncertain classifications to increase predictive
accuracy iteratively; 3) a semi-automatic data-driven query generator to
create new search queries from existing reviewed citation data sets.\\
The framework was applied on an example topic performing citation
collection and screening. We estimated median posterior Sensitivity and
Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
predict the distribution of possibly missed relevant matches in the
unreviewed records.\\
17755 unique records were collected through the framework citation
manager; 101 over 766 records were found to be relevant after manual
evaluation, while the rest were excluded by the automatic
classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
generated from the labelled dataset, and 82579 more records were
collected. Only 567 records required human review after the automatic
screening, and six additional positive matches were found. Including the
additional records, the overall expected Sensitivity dropped to 97.3\%
{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
98.7\%{]}.\\
The framework can significantly reduce human resources requirements for
systematic reviews by simplifying citation collection and screening
while demonstrating exceptional sensitivity even on large data sets.
\end{abstract}

@@

The labeled records were used to train the Bayesian classification model
used to label the remaining records. After seven classification and
review (CR) iterations (three resulting in new positive matches and four
extra replications to account for stochastic variability), a total of
101 positives matches were found, requiring manual review of 766 records
(13.2\% positivity rate).\\
It is possible to observe how the number of records that required manual
review dropped rapidly between iterations (Table 2), indicating that the
engine was converging while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2, showing the mixture distribution of the PPDs of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinked
(they concentrate in a shorter probability range) and shifted toward the
negative zone as more positive matches are found and reviewed.

@@

\caption{\label{tab:Table 2}\textbf{Table 2}. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrlrrrrrr}
\toprule
Session & Iteration & Positives & Negatives & Total labelled (\%) & Unlab. -> y & Unlab. -> n & Unlab. -> * & n -> y & Changes & N. features\\
\midrule
\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2289}\\
 & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2289\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3750}\\
 & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3834\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3856}\\
\addlinespace
 & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3856\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3856}\\
 & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3856\\
\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1273} & \cellcolor{gray!6}{4729}\\
 & 2 & 107 & 1123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4729\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4733}\\
 & 4 & 107 & 1200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4729\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4729}\\
 & 6 & 107 & 1226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4729\\
\bottomrule
\end{tabular}}
\end{table}

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) as well as the region of
interest (``Orange County'') of another research group active on the
topic of healthcare asociated pathogen spreading over hospital networks.
Some terms were considered highly relevant for the BART models (e.g.,
``Worker'' in 6th position out of more than 3800 terms considered)
although in a simpler linear model their effect would be hardly
significant (statistic: -1.21 s.e.); these are terms which are relevant
only in conjunction with other terms but not by themselves, highlighting
the extra predictive power brought by a non-linear model like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

The new search produced 107294 records (Table 1), of which 48396
(58.6\%) from the EMBASE, followed by 28811 (34.9\%) from Pubmed, 17070
(20.7\%) from SCOPUS, 12956 (15.7\%) from WOS, and 61 (0.074\%) from
IEEE; compared with the first session, the relative weight of EMBASE and
Pubmed was decreased, while the amount of content specificity was
greatly increased, as it was for SCOPUS. After removal of duplicates,
82579 unique records were obtained. Once joined with the session 1
records and duplicates removed, we obtained 98371 unique records, with
just 1963 shared records between searches, that is the 2\%. The
percentage of records shared by two or more source dropped to 22\%.

Six CR rounds were necessary to complete the second session
classification, with just 6 new positive found after reviewing 568 extra
records. The first CR iteration required the user to review a
substantial number of records (1,273), but just labelling 275 of them
(the canonical 250 plus 25 that were already labelled during the
framework hyperparameter tuning) was sufficient to drop this number to
just 190 in the subsequent round. An evaluation of the convergence
(Figure 1, Supplemental Material S2) showed that, in addition to the
dynamics already observed in session 1 (shrinkage and negative shift), a
second mode appeared in the mixture distribution of the records to be
reviewed, centred in a highly positive zone. The interpretation is that
as the number of negative training records increases, the engine gets
more and more skeptical and asks to review even some records labelled as
positive in the initial training set generated during Session 1. This
behaviour can be useful to spot classification errors and
inconsistencies. Considering both sessions, 1333 records were reviewed
and 107 (8.03\%) were found.

Again, the evaluation of the inclusion rate of the terms showed that the
engine was quite capable of internalizing the concepts behind the
research topic A subsample of the terms is reported in Table 2 of
Supplemental Material S2.

@@

As described in the methods, the selection of hyperparameters was
achieved via evaluation of sensibility and efficiency through a grid
search on a validation set of 1200 completely manually labelled records.
The best set of parameters suggested an initial input of 250 labelled
records with 10x positive matches oversampling, an averaged ensemble of
10 models, no bootstrapping and an uncertainty zone defined by the 98\%
predictive interval. On the validation set, this combination of
parameters reached a sensitivity of 98.8\% (81 / 82 positive matches
found) and efficiency of 61.5\% (462 / 1200 records evaluated). The
results of the hyperparameter tuning are reported in Table 3 of
Supplemental Material S2. Figure 2 in Supplemental Material S2
demonstrates that the positive record oversampling rate, the number of
ensemble models and the size of the initial training set were the
parameters that most impact performance.

@@

To evaluate the theoretical performance of the engine, a surrogate
Bayesian logistic regression model was trained on the manually reviewed
labels using only the lower bound of the record PPDs as predictor (see
Methods for details). The surrogate model show the high predictive power
of the scores produced by the classification model (Bayesian R2: 98.1\%
{[}97.4\%, 98.3\%{]} for session 1 and 98.2\% {[}97.6\%, 98.3\%{]} for
session 2).\\

Figure 2 presents the actual and predicted (from the surrogate model)
cumulative number of positive matches, ordered by the initial simple
ordering query: the median of surrogate models' cumulative predictive
distributions matches quite well the actual number of positive records
found. It is striking how many more records would have needed to be
evaluated manually to find the same number of positive matches without
using a smart classification tool; some relevant record was found even
close to the end of the heuristically ordered list of records.\\

Table 3 shows various performance indexes for both sessions, both
descriptive (Total records, Reviewed records, Observed positive matches)
and estimated through the surrogate model (Expected efficiency,
Predicted positive matches, Expected sensitivity, \(R^2\)).\\
In session 1 we observe an expected total number of positives of 101
{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
and efficiency of 95.7\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
a drop in the expected sensitivity, especially in the lower margin
(97.3\% {[}73.8\%, 100\%{]}), due to the fact that as the number of
records grows, even a small probability can translate, in the worst case
scenario, into a relevant number of missed positive matches (145 in this
case). To ascertain that no evident positives were missed, we evaluated
100 more records between the unreviewed ones with the highest median
predicted probability produced by the engine and found no additional
positive matches.\\

@@

\caption{\label{tab:Table 3}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals.}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}

@@

We propose a new integrated framework to help researchers collect and
screen scientific publications characterised by high performance and
versatility, joining the growing field of systematic review automation
(SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
et al. 2009; O'Mara-Eves et al. 2015). This framework joins standard
approaches and uses ad-hoc solutions to deal with common SRA issues. By
freely sharing the tool as an open-source R package and by following a
modular design, we tried to adopt some of the so-called Vienna
Principles advocated by the International Collaboration for the
Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
The framework consists of four main components: 1) an integrated
query-based citation search and management engine, 2) a Bayesian active
machine learning-based citation classifier, and 3) a data-driven search
query generation algorithm.\\

The framework's search engine module is capable of automatically
collecting citation data from three well-known scientific databases
(i.e., Pubmed, Web of Science, and the database of the Institute of
Electrical and Electronics Engineers) as well as process manually
downloaded results from both the mentioned and other (SCOPUS, EMBASE)
databases. In comparison, most SRH tools, commercial or free to use,
rely either on internal databases (e.g., Mendeley
\url{https://www.mendeley.com/}) sometimes focusing just on a particular
topic (Visser 2010) or on a single external data source (Thomas and
Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
2019).\\
Mixing different databases is fundamental to have a more comprehensive
view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
positive matches found were unique for one of the different data
sources, and no positive record was present in all of them (data not
shown).\\
The online search algorithms are efficient enough to manage tens of
thousands of search results, using various expedients to overcome the
limitations of the queried databases in terms of traffic and download
quota. The results are then automatically organized, deduplicated and
arranged by ``simple query ordering'' in a uniform corpus. The
preliminary ordering allow to increase the positivity rate in the
initial training set (Wallace, Small, et al. 2010).\\

>>>>

\author{
    Angelo D'Ambrosio
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:angelo.d.ambrosio@uniklinik-freiburg.de}{\nolinkurl{angelo.d.ambrosio@uniklinik-freiburg.de}};
\href{mailto:a.dambrosioMD@gmail.com}{\nolinkurl{a.dambrosioMD@gmail.com}}} \\
   \And
    Hajo Grundmann
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
   \And
    Tjibbe Donker
   \\
    Institute for Infection Prevention and Hospital Hygiene \\
    Freiburg University Hospital \\
  Freiburg, Germany \\
  \texttt{\href{mailto:tjibbe.donker@uniklinik-freiburg.de}{\nolinkurl{tjibbe.donker@uniklinik-freiburg.de}}} \\
  }

@@

\begin{abstract}
The exponential growth in scientific production makes its summarisation
through secondary literature exceedingly demanding in terms of time and
human resources. We introduce a new open-source framework that
significantly increases efficiency during the citation collection and
screening phases of systematic reviews.\\
The framework introduces three main tools: 1) an automatic citation
search engine and manager that allows collecting records from multiple
citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified
query syntax; 2) a citation screening tool based on Bayesian active
machine learning and natural language processing, which requires users
feedback only on uncertain classifications to increase predictive
accuracy iteratively; 3) a semi-automatic data-driven query generator to
create new search queries from existing reviewed citation data sets.\\
The framework was applied on an example topic performing citation
collection and screening. We estimated median posterior Sensitivity and
Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
predict the distribution of possibly missed relevant matches in the
unreviewed records.\\
17755 unique records were collected through the framework citation
manager; 101 over 766 records were found to be relevant after manual
evaluation, while the rest were excluded by the automatic
classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
generated from the labelled dataset, and 82579 more records were
collected. Only 567 records required human review after the automatic
screening, and six additional positive matches were found. Including the
additional records, the overall expected Sensitivity dropped to 97.3\%
{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
98.7\%{]}.\\
The framework can significantly reduce human resources requirements for
systematic reviews by simplifying citation collection and screening
while demonstrating exceptional sensitivity even on large data sets.
\end{abstract}

@@

The labeled records were used to train the Bayesian classification model
used to label the remaining records. After seven classification and
review (CR) iterations (three resulting in new positive matches and four
extra replications to account for stochastic variability), a total of
101 positives matches were found, requiring manual review of 766 records
(13.2\% positivity rate).\\
It is possible to observe how the number of records that required manual
review dropped rapidly between iterations (Table 2), indicating that the
engine was converging while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2, showing the mixture distribution of the PPDs of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinked
(ie., gets concentrated in a shorter probability range) and shifted
toward the negative zone as more positive matches are found and
reviewed.

@@

\caption{\label{tab:Table 2}\textbf{Table 2}. Results of the automatic classification and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrlrrrrrr}
\toprule
Session & Iteration & Positives & Negatives & Total labelled (\%) & Unlab. -> y & Unlab. -> n & Unlab. -> * & n -> y & Changes & N. features\\
\midrule
\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2289}\\
 & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2289\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3750}\\
 & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3834\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3856}\\
\addlinespace
 & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3856\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3856}\\
 & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3856\\
\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1273} & \cellcolor{gray!6}{4729}\\
 & 2 & 107 & 1123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4729\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4733}\\
 & 4 & 107 & 1200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4729\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4729}\\
 & 6 & 107 & 1226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4729\\
\bottomrule
\end{tabular}}
\end{table}

@@

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research
topic, i.e., ``patient transport'' or ``transfer'' through a ``network''
of ``facility''ies that facilitates the ``spread'' of infections, and
even one of the authors of this study (Donker T.) as well as the region
of interest (``Orange County'') of another research group active on the
topic of pathogen spreading over hospital networks. Some terms were
considered highly relevant by the BART models (e.g., ``Worker'' in 6th
position out of more than 3800 terms considered) although in a simpler
linear model their effect would be hardly significant (statistic: -1.21
s.e.); these are terms which are relevant only in conjunction with other
terms but not by themselves, highlighting the extra predictive power
brought by using advanced, non-linear machine learning.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

@@

The new search produced 107294 records (Table 1), of which 48396
(58.6\%) from the EMBASE, followed by 28811 (34.9\%) from Pubmed, 17070
(20.7\%) from SCOPUS, 12956 (15.7\%) from WOS, and 61 (0.074\%) from
IEEE; compared with the first session, the relative weight of EMBASE and
Pubmed was decreased, while the amount of content specificity was
greatly increased, as it was for SCOPUS. After removal of duplicates,
82579 unique records were obtained. Once joined with the session 1
records and removal of duplicates, we obtained 98371 unique records,
with just 1963 shared records between searches, that is the 2\%. The
percentage of records shared by two or more source dropped to 22\%.

Six CR rounds were necessary to complete the second session
classification, with just 6 new positive found after reviewing 568 extra
records. The first CR iteration required the user to review a
substantial number of records (1,273), but just labelling 275 of them
(the canonical 250 plus 25 that were already labelled during the
framework hyperparameter tuning) was sufficient to drop this number to
just 190 in the subsequent round. An evaluation of the convergence
(Figure 1, Supplemental Material S2) showed that, in addition to the
dynamics already observed in session 1 (shrinkage and negative shift), a
second mode appeared in the mixture distribution of the records to be
reviewed, centred in a highly positive zone. The interpretation is that
as the number of negative training records increases, the engine gets
more and more skeptical and asks to review even some records labelled as
positive in the initial training set generated during Session 1. This
behaviour can be useful to spot classification errors and
inconsistencies. Considering both sessions, 1333 records were manually
reviewed and 107 (8.03\%) confirmed positive matches were found.

Again, the evaluation of the inclusion rate of the terms showed that the
engine was quite capable of internalizing the concepts behind the
research topic A subsample of the relevant terms used by the model in
the second session is reported in Table 2 of Supplemental Material S2.

@@

As described in the methods, the selection of hyperparameters was
achieved via evaluation of sensibility and efficiency through a grid
search on a validation set of 1200 manually labelled records. The
analysis suggested the following combination of parameters as the best
performing: an initial input of 250 labelled records with 10x positive
matches oversampling, an averaged ensemble of 10 models, no
bootstrapping and an uncertainty zone defined by the 98\% predictive
interval. This combination of parameters was associated with a
sensitivity of 98.8\% (81 / 82 positive matches found) and efficiency of
61.5\% (462 / 1200 records evaluated). The detailed results of the
hyperparameter tuning ananlysis are reported in Table 3 of Supplemental
Material S2. Figure 2 in Supplemental Material S2 demonstrates that the
positive record oversampling rate, the number of ensemble models and the
size of the initial training set were the parameters that mostly
impacted performance.

@@

To evaluate the theoretical performance of the engine, a surrogate
Bayesian logistic regression model was trained on the manually reviewed
labels using only the lower bound of the record PPDs as predictor (see
Methods for the details). The surrogate model showed the high predictive
power of the scores produced by the classification model (Bayesian R2:
98.1\% {[}97.4\%, 98.3\%{]} for session 1 and 98.2\% {[}97.6\%,
98.3\%{]} for session 2).\\

Figure 2 presents the actual and predicted (from the surrogate model)
cumulative number of positive matches, ordered by the initial simple
ordering query: the median of surrogate models' cumulative predictive
distributions matches quite well the actual number of positive records
found. It is striking how many more records would have needed to be
evaluated manually to find the same number of positive matches without
using a smart classification tool, with some positive matches found
close to the end of the heuristically ordered list of records.\\

Table 3 shows various performance indexes for both sessions, both
descriptive (Total records, Reviewed records, Observed positive matches)
and estimated through the surrogate model (Expected efficiency,
Predicted positive matches, Expected sensitivity, \(R^2\)).\\
In session 1 we observe an expected total number of positives of 101
{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
and efficiency of 95.6\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
a drop in the expected sensitivity, especially in the lower credibility
boundary (97.3\% {[}72.8\%, 100\%{]}), due to the fact that as the
number of records grows, even a small probability of being a positive
match can translate, in the worst case scenario, into a relevant number
of missed positive matches (147 in this case). To ascertain that no
evident positives were missed, we evaluated 100 more records between the
unreviewed ones with the highest median predicted probability produced
by the engine and found no additional positive matches.\\

@@

\caption{\label{tab:Table 3}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals.}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 766 (4.31\%) & 1333 (1.36\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.6\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.1\%, 98.6\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 147]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [72.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}

@@

We propose a new integrated framework to help researchers collect and
screen scientific publications characterised by high performance and
versatility, joining the growing field of systematic review automation
(SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
et al. 2009; O'Mara-Eves et al. 2015). This framework implements
standard approaches and uses ad-hoc solutions to deal with common SRA
issues. By freely sharing the tool as an open-source R package and by
following a modular design, we tried to adopt some of the so-called
Vienna Principles advocated by the International Collaboration for the
Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
The framework consists of four main components: 1) an integrated
query-based citation search and management engine, 2) a Bayesian active
machine learning-based citation classifier, and 3) a data-driven search
query generation algorithm.\\

The framework's search engine module is capable of automatically
collecting citation data from three well-known scientific databases
(i.e., Pubmed, Web of Science, and the database of the Institute of
Electrical and Electronics Engineers) as well as process manually
downloaded results from both the two more (SCOPUS, EMBASE) databases. In
comparison, most SRH tools, commercial or free to use, rely either on
internal databases (e.g., Mendeley \url{https://www.mendeley.com/})
sometimes focusing just on a particular topic (Visser 2010) or on a
single external data source (Thomas and Brunton 2007; Poulter et al.
2008; Soto, Przybyła, and Ananiadou 2019).\\
Mixing different databases is fundamental to have a more comprehensive
view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
positive matches found only in one of the different data sources, and no
positive record was present in all of them (data not shown).\\
The online search algorithms are efficient enough to manage tens of
thousands of search results, using various expedients to overcome the
limitations of online citation databases in terms of traffic and
download quotas. The results are then automatically organized,
deduplicated and arranged by ``simple query ordering'' in a uniform
corpus. The preliminary ordering allows to increase the positivity rate
in the initial training set (Wallace, Small, et al. 2010).\\

For the framework's record classification module, we employed an active
machine learning approach Miwa et al. (2014) based on the best practices
from other SRA studies but also bringing further improvements at various
levels.\\
The feature extractor module uses modern NLP techniques (Ananiadou and
McNaught 2006; K. B. Cohen and Hunter 2008) to transform text into input
data for machine learning. We did not include classical n-grams
(Schonlau and Guenther 2017), but we used network analysis to find
non-consecutive frequently associated terms, a generalisation of n-grams
relaxing the term adjacency assumption. This approach allows also to
find term connections across fields, for example a term having a
different relevancy if associated with a specific author. The same
technique but with different parameters was applied to merge redundant
terms to make model estimation more efficient and reduce noise.\\
The use of concurrency network-driven modelling of text is not new
(Francois Rousseau 2015; Violos et al. 2016; François Rousseau, Kiagias,
and Vazirgiannis 2015; Ohsawa, Benson, and Yachida 1998) and is a
valuable tool to extract semantic information not evident in one-word or
consecutive n-gram models.\\
